{\normalsize Seminar: Formal Specification} \\[1ex] Security of Multithreaded Programs by Compilation\cite{Barthe07}

### 2012-01-26 paper/paper.tex
removed todo about mathpartir
used minipaged in advanced typing rules to save space
exlained intution of eval beautified eval removed todo
corrected spelling

\todo{explain intuition?}
\begin{align*}
s, h \Downarrow_{conc} \mu \Leftrightarrow \exists s', h'. s,h \leadsto_{conc}^* s',h' \land s'.act = \emptyset \land s'.gmem = \mu
\end{align*}

@@

A program is typeable in this type system $\mathcal{S}, se \vdash P$, where a function $\mathcal{S}:
\mathcal{P} \rightarrow \text{LType}$ that maps a local type to every program point
and a security environment $se$, iff $\mathcal{S}$ maps every initial program point
(including the ones of spawned threads) to $\textsc{t}_{init}$ and for every program point $j$ which is an
successor of $i$ there is a type $s \in \text{LType}$, such that $\textsc{s}$ is lower bounded
by $\mathcal{S}(j)$ and $se, i \vdash \mathcal{S}(i) \Rightarrow \textsc{s}$ holds.

@@

\todo{use an other package to display these rules}
\begin{figure}
\begin{align*}
\inferrule[L-Cond]{\vdash e : L \\ \vdash_\alpha c : E \\ \vdash_\alpha c' : E}
{\vdash_\alpha [\text{if} \ e \ \text{then} \ c \ \text{else} \ c']^n_\alpha : E}
\end{align*}

\begin{align*}
\inferrule[H-Cond]{\vdash e : H \\ \vdash_\bullet c : E \\ \vdash_\bullet c' : E}
{\vdash_\bullet [\text{if} \ e \ \text{then} \ c \ \text{else} \ c']^n_\bullet : E}
\end{align*}

>>>>

\begin{align*}
s, h \Downarrow_{conc} \mu \Leftrightarrow \exists s', h'.\ (s,h \leadsto_{conc}^* s',h') \land s'.act = \emptyset \land s'.gmem = \mu
\end{align*}

So the state $s$ evaluates according to a history $h$ to a final global memory $\mu$ iff there is a
sequence of concurrent executions that terminates (i.e. there are no active threads) and has the
global memory $\mu$.

@@

A program is typeable in this type system (written $\mathcal{S}, se \vdash P$),
where $\mathcal{S}$ is a function $\mathcal{S}: \mathcal{P} \rightarrow \text{LType}$
that maps a local type to every program point
and $se$ a security environment, iff $\mathcal{S}$ maps every initial program point
(including the ones of spawned threads) to $\textsc{t}_{init}$ and for every program point $j$ which is an
successor of $i$ there is a type $s \in \text{LType}$, such that $\textsc{s}$ is lower bounded
by $\mathcal{S}(j)$ and $se, i \vdash \mathcal{S}(i) \Rightarrow \textsc{s}$ holds.

@@

\begin{figure}
\begin{minipage}{.5\textwidth}
\begin{align*}
\inferrule[L-Cond]{\vdash e : L \\ \vdash_\alpha c : E \\ \vdash_\alpha c' : E}
{\vdash_\alpha [\text{if} \ e \ \text{then} \ c \ \text{else} \ c']^n_\alpha : E}
\end{align*}
\end{minipage}
\begin{minipage}{.5\textwidth}
\begin{align*}
\inferrule[H-Cond]{\vdash e : H \\ \vdash_\bullet c : E \\ \vdash_\bullet c' : E}
{\vdash_\bullet [\text{if} \ e \ \text{then} \ c \ \text{else} \ c']^n_\bullet : E}
\end{align*}
\end{minipage}
